Draft -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- Draft

### 2024-09-02 index.qmd
resampling saved

## Impact of the vegetation cover on the prediction

@@

```{r Resampling}

@@

a <- list.files("Data/Resampling", recursive = T) %>% 
  as_tibble() %>% 
  rename(path = "value") %>% 
  mutate(name = gsub(".*/","",path) %>% gsub(".tif","",.)) %>% 
  pull(name) %>%
  str_c(collapse = "\", \"") %>%
  str_c("\"", ., "\"")

@@

write.csv(a, 
  "test.csv")

>>>>

## Impact of the spatial resolution in the prediction
## Impact of the vegetation cover on the prediction

@@

```{r Resampling orthos}
#| cache: false
#| echo: false
#| warning: false
#| eval: false

@@

a <- list.files("D:/Git_repo/DISCOV-MicaSense/Data/img") %>% 
  as_tibble() %>% 
  rename(path = "value") %>% 
  mutate(name = gsub(".*/","",path) %>% gsub(".tif","",.)) %>% 
  # dplyr::filter(str_detect("Arz_29092022_Fl2_12m*", name))
  pull(name) %>%
  str_c(collapse = "\", \"") %>%
  str_c("\"", ., "\"")

@@

write.csv(a, 
  "test.csv")
```

```{r gif_making}

list_pred <- list.files("Data/Predictions/Resampled",full.names = T) %>% 
  as_tibble() %>% 
  rename(path = "value") %>% 
  mutate(name = gsub(".*/","",path),
         type = case_when(str_detect(name, "_prob.tif") ~ "Prob",
                          T ~ "Pred")) %>% 
  dplyr::filter(type == "Pred") %>% 
  mutate(res =sub(".*_(\\d+)cm_.*", "\\1", name) %>% as.numeric(),
         ortho_name  = sub("_(\\d+)cm_.*", "", name)) %>% 
  arrange(ortho_name,res) %>% 
  mutate(site = case_when(str_detect(ortho_name, "Aveiro_1506_Highest") ~ "Aveiro",
                          str_detect(ortho_name, "Aveiro_boat_1706_flight_1") ~ "Boat1",
                          str_detect(ortho_name, "Aveiro_boat_1706_flight_2") ~ "Boat2",
                          str_detect(ortho_name, "NoirmoutierNorthDikeSite") ~ "NorthDike",
                          str_detect(ortho_name, "Duer_15072022_120m") ~ "Duer",
                          str_detect(ortho_name, "handfisher_Ortho") ~ "handfisher_Ortho",
                          str_detect(ortho_name, "Horse_rooster") ~ "Horse_rooster",
                          str_detect(ortho_name, "fl1_120m_handfisher_old") ~ "fl1_120m_handfisher_old",
                          str_detect(ortho_name, "fl2_120m_handfisher_old") ~ "fl2_120m_handfisher_old",
                          T ~ NA)) %>% 
  dplyr::filter(!site == "handfisher_Ortho",
                !site == "Duer")

scales <- data.frame(res = unique(list_pred$res)) %>% 
  mutate(label = case_when(res < 100 ~  paste0(res, "cm"),
                           T ~ paste0(res / 100, "m")))
extremes <- data.frame(
  res = c(10, 3000),
  label = c("10cm", "30m")
)

for(i in 1 :nrow(scales)){

 point_of_interest <- scales[i,]

 a <- ggplot() +
  theme_void()+
  # Draw the axis as a line
  geom_segment(aes(x = 10, xend = 3000, y = 0, yend = 0), linewidth = 0.5) +

  # Add the points at the extremities with labels
  geom_text(data = extremes, aes(x = res, y = 0, label = label), vjust = -1, size = 5) +

  # Add the point of interest with a label
  geom_point(data = point_of_interest, aes(x = res, y = 0), color = "red", size = 3) +
  geom_text(data = point_of_interest, aes(x = res, y = 0, label = label), vjust = 1.5, size = 5, color = "red") +

  # Scale the x-axis from 10 to 3000 cm
  # scale_x_continuous(limits = c(10, 3000), breaks = c(10, 100, 500, 1000, 1500, 2000, 2500, 3000)) +

  # Customize the theme to remove y-axis
  # theme_minimal() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )

 ggsave(paste0("output/plot/scales/",point_of_interest$res,".png"),a, bg = "white",width = 1904*2, height = 132*2, unit = "px" )

for(i in 1:nrow(list_pred)){

    img <- list_pred$path[i] %>% 
      rast() 
    names(img) <- "layer"

    img <- img %>% 
       dplyr::filter(layer != 0,
                     layer <= 8) %>% 
      mutate(layer = as.factor(layer))
    # ifel(img$layer == 0 | img$layer > 8, NA, img$layer)

     if(list_pred$site[i] == "Aveiro"){
       mask <- read_sf("Data/shp/Aveiro/background_Gafanha_high.shp") %>% 
         dplyr::filter(Type != "Land")
     }else{
       if(list_pred$site[i]  %in% c("Boat1","Boat2")){
         mask <- read_sf("Data/shp/Aveiro/background_Boat.shp") %>% 
          dplyr::filter(Type != "Land")
       }else{
         if(list_pred$site[i] == "NorthDike"){
           mask <- read_sf("Data/shp/Bourgneuf/background_Dike.shp") %>% 
            dplyr::filter(Type != "Land")
         }else{
           if(list_pred$site[i] == "Horse_rooster"){
             mask <- read_sf("Data/shp/Aveiro/background_Horse_rooster.shp") %>% 
                dplyr::filter(Type != "Land")
           }else{
            if(list_pred$site[i]  %in% c("fl1_120m_handfisher_old","fl2_120m_handfisher_old")){
              mask <- read_sf("Data/shp/Bourgneuf/background_fisherman.shp") %>% 
              dplyr::filter(Type != "Land")
            }
           }
          }
        }
     }

    low_res <-  list_pred %>% 
      dplyr::filter(site == list_pred$site[i],
                    res == max(res)) %>% 
      pull(path) %>% 
      rast()

    names(low_res) <- "layer"

    low_res <- low_res %>% 
       dplyr::filter(layer != 0,
                     layer <= 8) %>% 
      mutate(layer = as.factor(layer))

     img <- mask(img,mask)

     df_layer <- img %>% 
      as_tibble() %>% 
      # mutate(layer = as.numeric(layer)) %>%
      filter(!is.na(layer),
             layer != 0 ) %>%
      group_by(layer) %>%
      summarise(count = n()) %>%
      mutate(percentage = count / sum(count) * 100,
             label = paste0(layer, " (", round(percentage, 1), "%)"))

    colors <- data.frame(
      layer = as.character(c(1:5)),
      color = c("#DAA520","#b3ff1a","#389318","#873e23","#b3002d")
    )

    layer_counts <- df_layer %>% 
      mutate(layer = as.character(layer)) %>%
      # dplyr::filter(layer %in% c("3","4") ) %>% 
      select(layer,count) %>% 
      dplyr::filter(layer %in% c("1","2","3","4","5")) %>% 
      left_join(colors, by = "layer")

    png("pie_chart.png", width = 800, height = 800, bg = "transparent")

    plotrix::pie3D(layer_counts$count,
      # labels = layer_counts$layer,
      explode = 0.1, # Adds space between the slices
      # main = "3D Pie Chart of Layer",
      col = layer_counts$color,
      radius = 0.5,
      theta = 2)

    dev.off()

    img_grob <- grid::rasterGrob(png::readPNG("pie_chart.png"), 
                             interpolate = TRUE)

    scale_grob <- grid::rasterGrob(png::readPNG(paste0("Output/plot/scales/",list_pred$res[i],".png")), 
                             interpolate = TRUE)

   plot <-  ggplot()+
        tidyterra::geom_spatraster(data = img, 
                                   mapping = aes(fill = layer),
                                   maxcell = 500832*8)+
     tidyterra::geom_spatraster(data = low_res, 
                                   mapping = aes(fill = layer), 
                                alpha = 0)+

      coord_sf(crs = 4326)+
      scale_fill_manual(breaks = c(1,2,3,4,5,6,7,8),
                        values=c("#DAA520", "#b3ff1a","#389318","#873e23","#b3002d","#797a79","white","#42c9bc"),
                        na.value = NA,
                        name = "",
                        labels = c("Bacillariophyceae",
                                   "Chlorophyceae",
                                   "Magnoliopsida",
                                   "Phaeophyceae",
                                   "Rhodophyceae",
                                   "Sediment",
                                   "Sunglint",
                                   "Water"))+
     theme_Bede_Map()+
     theme(axis.text.x = element_text(size = 20, angle = 20,hjust = 1),
           axis.text.y = element_text(size = 20),
           axis.title = element_blank(),
           legend.background = element_blank(),
           legend.text = element_text(size = 20),
           legend.key.size = unit(1,"cm"))

   plot_limits <- ggplot_build(plot)$layout$panel_params[[1]]

    x_range <- plot_limits$x_range
    y_range <- plot_limits$y_range

   if(list_pred$site[i] == "Aveiro"){
      x_position_1 <- x_range[2] - (x_range[2] - x_range[1]) * 0.4
      y_position_1 <- y_range[1] + (y_range[2] - y_range[1]) * 0.4

      x_position_2 <- x_range[2] - (x_range[2] - x_range[1]) * 1
      y_position_2 <- y_range[1] + (y_range[2] - y_range[1]) * 0.1

      plot <- plot + annotation_custom(
          grob = img_grob,xmin = x_position_1,xmax = x_range[2], ymin = y_range[1], ymax = y_position_1)+
        theme(legend.position = c(0.91,0.6))+
         annotation_custom(
          grob = scale_grob,xmin = x_position_2,xmax = x_range[2], ymin = y_range[1], ymax = y_position_2)+
        theme(legend.position = c(0.91,0.6))

   if(list_pred$site[i] == "Boat1"){
      x_position_1 <- x_range[2] - (x_range[2] - x_range[1]) * 1.15
      x_position_12 <- x_range[2] - (x_range[2] - x_range[1]) * 0.7
      y_position_1 <- y_range[1] + (y_range[2] - y_range[1]) * 0.4
      y_position_12 <- y_range[1] + (y_range[2] - y_range[1]) * 0.8

      x_position_2 <- x_range[2] - (x_range[2] - x_range[1]) * 1
      y_position_2 <- y_range[1] + (y_range[2] - y_range[1]) * 0.1

      plot <- plot + 
        annotation_custom(grob = img_grob,
                          xmin = x_position_1,
                          xmax = x_position_12,
                          ymin = y_position_1, 
                          ymax = y_position_12)+
         annotation_custom(grob = scale_grob,
                           xmin = x_position_2,
                           xmax = x_range[2],
                           ymin = y_range[1],
                           ymax = y_position_2)+
        theme(legend.position = c(0.18,1))

   if(list_pred$site[i] == "Boat2"){
      x_position_1 <- x_range[2] - (x_range[2] - x_range[1]) * 0.9
      x_position_12 <- x_range[2] - (x_range[2] - x_range[1]) * 0.6
      y_position_1 <- y_range[1] + (y_range[2] - y_range[1]) * 0.6
      y_position_12 <- y_range[1] + (y_range[2] - y_range[1]) * 1

      x_position_2 <- x_range[2] - (x_range[2] - x_range[1]) * 1
      y_position_2 <- y_range[1] + (y_range[2] - y_range[1]) * 0.1

      plot <- plot + 
        annotation_custom(grob = img_grob,
                          xmin = x_position_1,
                          xmax = x_position_12,
                          ymin = y_position_1,
                          ymax = y_position_12)+
         annotation_custom(grob = scale_grob,
                           xmin = x_position_2,
                           xmax = x_range[2],
                           ymin = y_range[1],
                           ymax = y_position_2)+
        theme(legend.position = c(0.18,1))

   }
   if(list_pred$site[i] == "NorthDike"){
      x_position_1 <- x_range[2] - (x_range[2] - x_range[1]) * 0.9
      x_position_12 <- x_range[2] - (x_range[2] - x_range[1]) * 0.6
      y_position_1 <- y_range[1] + (y_range[2] - y_range[1]) * 0.6
      y_position_12 <- y_range[1] + (y_range[2] - y_range[1]) * 1

      x_position_2 <- x_range[2] - (x_range[2] - x_range[1]) * 1
      y_position_2 <- y_range[1] + (y_range[2] - y_range[1]) * 0.1

      plot <- plot + 
        annotation_custom(grob = img_grob,
                          xmin = x_position_1,
                          xmax = x_position_12,
                          ymin = y_position_1,
                          ymax = y_position_12)+
         annotation_custom(grob = scale_grob,
                           xmin = x_position_2,
                           xmax = x_range[2],
                           ymin = y_range[1],
                           ymax = y_position_2)+
        theme(legend.position = c(0.18,1))

    # plot
    ggsave(paste0("Output/Resampling/",gsub(".tif",".png",list_pred$name[i])), plot, height = 1125*4, width = 1320*4, units = "px")

}
```

```{r resampling validation data}
